Fourmile Calibrations

### 2023-01-31 calibration_output.Rmd
finished for meeting

@@

>>>>

## RD and RG

```{r rd and rg, echo = F}

gw_grid <- grid %>%
  dplyr::select(time, genRD1, genRD2, genRG1, genRG2) %>%
  mutate(source = 'grid')

gw_statn <- statn %>%
  dplyr::select(time, genRD1, genRD2, genRG1, genRG2) %>%
  mutate(source = 'statn')

gw <- bind_rows(gw_grid, gw_statn) %>%
  mutate(year = year(time)) %>%
  rename(date = time)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRD1)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRD1')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRD2)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRD2')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRG1)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRG1')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=genRG2)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('genRG2')

gw <- gw %>%
  group_by(year, source) %>%
  mutate(RD1cumsum = cumsum(genRD1),
         RD2cumsum = cumsum(genRD2),
         RG1cumsum = cumsum(genRG1),
         RG2cumsum = cumsum(genRG2))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD1cumsum)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRD1')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD2cumsum)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRD2')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG1cumsum)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRG1')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG2cumsum)) +
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative genRG2')

# HRU Map

@@

# Tmean for HRUs 7, 9, 22, 36

```{r hru7 temp, echo = F}

tmean7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t7_grid = tmean)

tmean7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t7_statn = tmean)

tmean9_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_9_grid.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t9_grid = tmean)

tmean9_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_9_statn.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t9_statn = tmean)

tmean22_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_22_grid.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t22_grid = tmean)

tmean22_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_22_statn.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t22_statn = tmean)

tmean36_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_36_grid.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t36_grid = tmean)

tmean36_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_36_statn.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t36_statn = tmean)

tmean_hrus <- list(tmean7_grid, tmean7_statn, tmean9_grid, 
     tmean9_statn, tmean22_grid, tmean22_statn,
     tmean36_grid, tmean36_statn)

t_hrus <- tmean_hrus %>% reduce(left_join, by='date')

t_hrus <- t_hrus %>%
  mutate(year = year(date)) %>%
  mutate(t7_diff = t7_statn - t7_grid,
         t9_diff = t9_statn - t9_grid,
         t22_diff = t22_statn - t22_grid,
         t36_diff = t36_statn - t36_grid) %>%
  group_by(year) %>%
  mutate(t7_cumdiff = cumsum(t7_diff),
         t9_cumdiff = cumsum(t9_diff),
         t22_cumdiff = cumsum(t22_diff),
         t36_cumdiff = cumsum(t36_diff))

tmean_cumdiff_plot <- ggplot(t_hrus, aes(x = date)) +
  geom_line(aes(y = t7_cumdiff, color = 'HRU7'), size =1) + 
  geom_line(aes(y = t9_cumdiff, color = 'HRU9'), size =1) + 
  geom_line(aes(y = t22_cumdiff, color = 'HRU22'), size =1) + 
  geom_line(aes(y = t36_cumdiff, color = 'HRU36'), size =1) + 
  facet_wrap(~year, scales = 'free') +
  scale_x_date(labels = date_format("%b")) +
  labs(y = 'Tmean cumulative difference (deg C)') +
  ggtitle('Tmean station and grid cumulative difference (Station - Grid)')

tmean_cumdiff_plot
